% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.
\documentclass[letterpaper,11pt]{article}
%-----------------------------------------------------------

\immediate\write18{git rev-parse --short HEAD > version.info }

%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{xcolor}
%\textheight=9.0in
\pagestyle{fancy}

\fancyhead{}
\fancyhead[RE,LO]{\textbf{\Large{Dominique Dierickx}}}
\fancyhead[LE,RO]{\href{https://www.dominiek.eu}{dominiek.eu}}
\fancyfoot{}
\fancyfoot[LE,LO]{\textcolor{gray}{\input{version.info}}}
\fancyfoot[RO, RE]{\thepage}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubheadingsimple}[1]{
	\textbf{#1} \\
	\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
	
	\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		
	\end{tabular*}
	
	\vspace{0.1in}
	\resheading{Facts}
	
	\begingroup
	\leftskip3em
	
	\begin{tabular*}{0.75\textwidth}{@{\extracolsep{\fill}} l l }
		Gender & Male \\
		E-mail address & \href{mailto:d.dierickx@gmail.com}{d.dierickx@gmail.com} \\
		Nationality & Belgian \\
		Mother tongue & Dutch  \\
	\end{tabular*}
	\\
	
	\endgroup

	\resheading{Work Experience}
	
	\begin{itemize}
		
		\item
		\ressubheading{Showpad}{Ghent}{Principal Software Engineer}{November 2019 - now()}
		 \break	 
		\begin{flushleft}
		I have been part of several teams, working on the core CMS capabilities of the Showpad SaaS platform. As a principal engineer, I am involved in designing and implementing new product features for our customers together with the teams and other stakeholders. We leverage AWS where appropriate to offer a scalable, cost-efficient and secure solution globally.
		
		Key skills: AWS, SaaS, Kotlin, TypeScript, ElasticSearch, ANTLR (\href{https://developer.showpad.com/docs/apis/content/showql}{ShowQL}), Security, Monitoring
		\end{flushleft}

		\item
		\ressubheading{Cegeka NV}{Ghent}{Application Architect}{January 2019 - November 2019}
		\break
		\begin{flushleft}
		As an Application Architect I was involved in the inception and development of a new platform for job candidate matching. Next to this, I also worked on requirement study, cost calculation and project presentations for prospects.
		
		Key skills: Java, Spring Boot, Kubernetes, OpenAPI, ElasticSearch
		\end{flushleft}		
		
		\item
		\ressubheading{TomTom NV}{Ghent}{Senior Software Architect in the Maps Unit}{January 2017 - January 2019}
		\begin{flushleft}
			As a software architect, I took the lead of the team designing and developing a new map delivery platform to replace a legacy (DVD-based) platform. This was developed in an API-first approach and is the main entrypoint for map customers. Next to this I was also involved in architectural decisions and guidelines within the unit.
			\break
			Key skills: Java, Spring Boot, OpenAPI, AWS, Redis, Kubernetes, Security
		\end{flushleft}
		
		\item
		\ressubheading{TomTom NV}{Ghent}{Expert Software Engineer in the Maps Unit}{January 2012 - January 2017}
		\begin{flushleft}
			As a software engineer, I worked in different teams responsible for transforming map data from one format and model to another. We leveraged Apache Hadoop and HBase in novel ways to allow faster and higher-quality map delivery to customers.
			\break
			Key skills: Java, Hadoop, HBase, Avro, Python, GIS, PostGIS, Data modeling
		\end{flushleft}
		
		\item
		\ressubheading{TomTom NV}{Ghent}{Software Engineer in the Research \& Development Unit}{February 2011 - December 2011}
		\begin{flushleft}
		Within the R\&D unit, I worked on internal and external research projects. This included working on different visualizations for dynamic map data (driving speeds, parking data, ...) and working together with partners within EU-funded projects to consume governmental or municipal API's to optimize routing and navigation experience.
		\break
		Key skills: Java, Spring Boot, Python, Kubernetes, OpenAPI, GIS, PostGIS
		\end{flushleft}
			\end{itemize}
		
		\pagebreak
		\hfill
			\begin{itemize}
			\vspace{0.2in}
		\item 
		\ressubheading{Adenti NV}{Zottegem}{Software developer}{September 2009 - January 2011}
		\begin{flushleft}
		I worked on developing a web-based (AJAX) front-end as well as backend solution for fleet tracking and insurance.
		\break
		Key skills: .NET, Silverlight, WCF, SQL Server, T-SQL
		\end{flushleft}
		
	\end{itemize}
			\vspace{-0.2in}
	\resheading{Education}
	\begin{itemize}
		
		\item
		\ressubheading{Vrije Universiteit Brussel}{Brussels}{Master in Applied Computer Science}{2007-2009}
		\begin{itemize}
			\resitem{Graduated with great honor}
			\resitem{Master's thesis: ``Supporting smart entity behavior across virtual environment platforms''}
		\end{itemize}
		
		\item
		\ressubheading{Koninklijk Technisch Atheneum Geraardsbergen}{Geraardsbergen}{Latin - Mathematics}{1998 - 2004}
		\\
		
		\item
		\ressubheading{Hogeschool Gent}{Ghent}{Bachelor in Applied Computer Science}{2004-2007}
		\begin{itemize}
			\resitem{Graduated with honor}
			\resitem{Internship at Ordina Belgium}
		\end{itemize}
		
	\end{itemize}
	
	\resheading{Skills Summary}
	
	\begin{description}
		\item[Languages:]
		Java, Kotlin, Python, Javascript, Typescript, (Unix) shell
		\item[Frameworks \& tools:]
		Spring (Boot), Micronaut, IntelliJ, VSCode, JUnit, Testcontainers, Docker, Amazon Web Services, Kubernetes, Datadog, Sentry
		\item[Databases:]
		PostgreSQL/PostGIS, MySQL, SQLite, ElasticSearch, OpenSearch
		\item[Principles:]
		API design \& documentation, event-driven, software architecture, DDD, CI/CD, testing, devops.
		\item[Interests:]
		Artificial intelligence, SaaS/API's, cybersecurity, Geospatial Information Systems (GIS), large-scale data solutions, algorithms
	\end{description}

	\resheading{In a nutshell}
	I am a driven, social person, interested in various fields and developments in computer science. My strongest points are my technical expertise, my eagerness to learn new things and my social skills. I have gained relevant experience through personal as well as professional projects and it is fair to say that software development is more of a passion than a profession in my life. In my spare time, I enjoy running, reading, experimenting with new technology and spending time with my wife and our two boys.
	\vspace{0.1in}
	
	\resheading{I am looking for}
	A position where I can make a difference and get things done. Working closely together with all stakeholders for the best possible outcome. In an environment that nurtures engineering culture, learning and knowledge sharing.
	
\end{document}